Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-16 special-issue-ci/Response to reviewers.tex

We thank the reviewer for the comment. The only reason why JavaScript
was chosen was because it is the only language that is native to the
browser, allowing to carry out precisely this kind of experiments
where the user is invited to click on an URL and start giving CPU to
it. Although there are many other volunteer frameworks, written in
other languages, that a priori would offer a higher performance, the
key is that they would {\em while they are running}, that is, as soon
as it has been installed, the user has decided to fire it up, and it
does not affect the performance in the rest of the system, which is a
concern in this kind of systems. We have performed speed tests on
JavaScript and other compiled languages resulting that, in fact,
JavaScript uses a JIT compiler that provides a good performance; we
have published these tests as an open access technical report. This
fact, along these explanations, have now been added to the first
paragraph of the {\em Description of the system} section.

JavaScript is probably the most popular language nowadays, and this
has inspired the appearance of many compilers, so that the fitness
function can, in fact, be written in any language and compiled to
JavaScript, as is shown in this list:
\url{https://github.com/jashkenas/coffeescript/wiki/list-of-languages-that-compile-to-js}. This
has also been added to the text.

In a nutshell, what we are saying is that, as is proven in the paper,
a JavaScript application, running in the browser, can gather in
seconds dozens of users. That would be, in practice, impossible with
other kind of native clients, who would have to download and maybe
compile the application, losing many seconds or minutes for the
optimization problem that has to be solved.

\begin{quote}
The paper organization is not clear. Some comments about this:
- The title "Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed
Evolutionary Computation" seems to suggest that the volunteers run in the cloud, but that is not the case:
the server run in the cloud and the volunteers do in the browsers of
common PCs and laptops.
\end{quote}

That is correct. We just used {\em cloud} in a relatively informal
sense because they are available as in a cloud for running the
experiment. That is, from the point of view of the person running the
experiment, there is a {\em cloud} out there running your experiments,
which is actually run by volunteers in their browsers. We went to the
original aception of ``cloud'' as a ``network'' more than the more
precise and technical aception used today.

We have added this explanation to the first paragraph in the
conclusions; we hope this makes our intention clearer, but we can also
eliminate that part of the title if the reviewer think it is
necessary.

\begin{quote}

- The paper abstract does not properly summarize the paper contents. It says that "That is why in this
paper we present NodIO, a client-server architecture for distributed evolutionary algorithms !", but there
are two versions of the architecture, as stated later in the conclusions: "In this paper two versions of a
client-server architecture for volunteer and distributed evolutionary !". That second version is neither
commented in the introduction.
\end{quote}

\begin{quote}
- According the last paragraph of the introduction, ÒThen, a detailed description of the proposed system is
presented in Section III, followed by the experiments and obtained results in Section IV.", but Section IV
does not only contains experimental result but also the full description of the second version of the
architecture.
Summarizing the review, the authors should provide a convincing example showing the advantages of
their proposal. As presented, the paper is a proof of concept of a system that seems difficult to be used
by the researchers needing high computational resources to run an evolutionary algorithm to solve a realworld
problem.
\end{quote}

### 2015-11-16 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Explains what we mean by "cloud"
Closes #32
Revising @fergunet comments
Related to issue #31, which he had not mentioned.

\begin{abstract}
Volunteer computing is used routinely in science and industry, but it
still has a long way to go if it is going to become a mainstream technology in the
same way the cloud technologies in general have. The lack of general
purpose and open source tools
with analytics built in could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present {\sf NodIO}, a client-server architecture for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser.  The architecture, along with some initial results on the
expected performance and scaling
behavior is presented. We also use the algorithm data to
find out what kind of patterns the user behavior follow and try to fit
them to some statistical distribution.
\end{abstract}

@@

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer frameworks written in compiled languages, such as C++ or Java, that can achieve more performance than JavaScript. However, one of the advantages of our system is that clients do not need to install anything in their machines, they just need to open a regular web page  
% Somewhat redundant 
% Javascript is the only language that can be executed in this way without any installation, 
% also removed the default, redundant with next sentence
in modern browsers, such as Chrome, Safari or Firefox, that are available in almost every desktop or mobile device. Other advantage is that the source code can be directly examined by the volunteer, not being compiled as other options (such as Java Applets or ActiveX). Also, as we discuss in this paper, it can provide some extra features such as enhanced security or operating system independence.

%PABLO: hay que enlazar con el siguiente párrafo
This kind of systems must solve a series of issues before even starting to 
measure their performance; these issues are related to security as well as
safety, which introduces a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.

@@

In this paper two versions of a client-server architecture for volunteer and distributed
evolutionary algorithms that uses the browser, termed {\sf NodIO} and
based on the {\sf NodEO} evolutionary algorithm library has been evaluated.

>>>>

\begin{abstract}
Volunteer computing is used routinely in science and industry, but it
still has a long way to go if it is going to become a mainstream technology in the
same way the cloud technologies in general have. The lack of general
purpose and open source tools
with analytics built in could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present {\sf NodIO}, a framework used to create client-server architectures for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser.  The architecture, along with some initial results on the
expected performance and scaling
behavior is presented. We also use the algorithm data to
find out what kind of patterns the user behavior follow and try to fit
them to some statistical distribution.
\end{abstract}

@@

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer frameworks written in compiled languages,
such as C++ or Java, that can achieve more performance than
JavaScript. However, one of the advantages of our system is that
clients do not need to install anything in their machines, they just
need to open a regular web page  
% Somewhat redundant 
% Javascript is the only language that can be executed in this way without any installation, 
% also removed the default, redundant with next sentence
in most browsers, such as Chrome, Safari or Firefox, that are
available in almost every desktop or mobile device. Other advantage is
that the source code can be directly examined by the volunteer, not
being compiled as other options (such as Java Applets, Flash scripts or
ActiveX). Also, as we discuss in this paper, it can provide some extra
features such as enhanced security or operating system independence.

%PABLO: hay que enlazar con el siguiente párrafo
Those desktop clients have also the same issues as any kind of
volunteer computing system, including our own:  these issues are
related to security as well as
safety, which introduces a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.

@@

In this paper two versions of a client-server architecture for volunteer and distributed
evolutionary algorithms that uses the browser and generated using {\sf
  NodIO}, based on the {\sf NodEO} evolutionary algorithm library have been
evaluated. Volunteers are {\em in the cloud}, as stated in the title,
since they are a {\em CPU as a service} for the persons running the
experiment. In fact, in this paper we have tried to put some figures
on the real size of that {\em cloud}.
